A new metric for automatic discovery of periodic patterns in time series

### 2021-02-28 paper/main.Rmd
minor addition on properties of wpd-norm

```{r dist-new-same-scale-link, fig.cap="wpd_perm$ and $wpd_{glm-scaled}$ are plotted together on the same scale. They also have the same location and hence the values from these two approaches could be compared across panels. $wpd_{glm-scaled}$ would be used to normalise $wpd_{raw}$ for higher $nx$ and $nfacet$ and $wpd_{glm-scaled}$ would be used for smaller levels to alleviate the problem of computational time."}
#
G21_permutation <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds")) %>%
  rename("wpd_permutation" = "value")

@@

\begin{equation}
wpd_{norm} =
\begin{cases}
wpd_{norm}^{perm},& \text{if } J, K <=5\\
wpd_{norm}^{glm-scaled},              & \text{otherwise}\\
\end{cases}
\end{equation}

>>>>

```{r dist-new-same-scale-link, fig.cap = "$wpd_perm$ and $wpd_{glm-scaled}$ are plotted together on the same scale. They also have the same location and hence the values from these two approaches could be compared across panels. $wpd_{glm-scaled}$ would be used to normalise $wpd_{raw}$ for higher $nx$ and $nfacet$ and $wpd_{glm-scaled}$ would be used for smaller levels to alleviate the problem of computational time."}

G21_permutation <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds")) %>%
  rename("wpd_permutation" = "value")

@@

\begin{equation}
wpd_{norm} =
\begin{cases}
wpd_{perm},& \text{if } J, K <=5\\
wpd_{glm-scaled},              & \text{otherwise}\\
\end{cases}
\end{equation}
